---
title: "REACT dashboard"
author: joe@databrew.cc
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---
  

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{r, results = 'hide'}
# Packages
library(ggplot2)
library(cism)
library(rgeos)
library(maptools)
library(rgdal)
library(tidyr)
library(RColorBrewer)
library(dplyr)
library(leaflet)
library(readr)
library(ggthemes)
library(ggrepel)
library(knitr)
library(kableExtra)
options(knitr.table.format = "html") 
# Define a theme
theme_maltem <- ggthemes::theme_hc
library(flexdashboard)

```

```{r}
# Get data
source('global.R')
```

Overview
=====================================  


Row
-----------------------------------------------------------------------

### Total malaria cases

```{r}
n <- sum(ts$value[ts$type == 'Case'], na.rm = TRUE)
flexdashboard::valueBox(n, icon = "fa-stethoscope", href = "#acd")
```

### Total cases treated

```{r}
n <- sum(ts$value[ts$type == 'Treated'], na.rm = TRUE)
flexdashboard::valueBox(n, icon = "fa-flag",
         color = 'info', href = "#acd")
```

### Total tests administered

```{r}
n <- sum(ts$value[ts$type == 'Tested'], na.rm = TRUE)
flexdashboard::valueBox(n, 
         icon = "fa-binoculars",
         color = 'warning', href = "#acd")
```


Row
-----------------------------------------------------------------------

### Cases at health facilities

```{r}
n <- sum(ts$value[ts$type == 'Case' & ts$location == 'HF'], na.rm = TRUE)
flexdashboard::valueBox(n, icon = "fa-vcard", color = 'warning', href = "#pcd")
```

### Cases from CHWs

```{r}
n <- sum(ts$value[ts$type == 'Case' & ts$location == 'CHW'], na.rm = TRUE)
flexdashboard::valueBox(n, icon = "fa-vcard", color = 'danger', href = "#pcd")
```

### Percent of all cases which are children < 5

```{r}
n <- ts %>% filter(type == 'Case') %>% group_by(age_group) %>% summarise(x = sum(value, na.rm = TRUE)) %>% mutate(p = x / sum(x) * 100) %>% filter(age_group == '< 5 years') %>% .$p %>% round(digits = 1)
flexdashboard::valueBox(n, icon = "fa-vcard", color = 'info', href = "#pcd")
```


    
Row
-------------------------------------
    
### Intervention area

```{r}
leaflet() %>%
  # addTiles() %>%
  addProviderTiles('Esri.WorldImagery') %>%
  addPolygons(data = cism::mag2, color = 'darkorange')
```

### Health facility locations

```{r}
mag_us <- cism::us %>%
  filter(district == 'MAGUDE')

leaflet() %>%
  # addTiles() %>%
  addProviderTiles('Stamen.Toner') %>%
  addPolylines(data = cism::mag2, color = 'darkorange') %>%
  addCircleMarkers(lng = mag_us$longitude,
                   lat = mag_us$latitude,
                   popup = mag_us$name)
```



Aggregate
=====================================  


Row
-----------------------------------------------------------------------

### All cases

```{r}
plot_data <- ts %>%
  filter(type == 'Case') %>%
  group_by(date) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'Cases')
```


### Underlying data

```{r}
prettify(plot_data, download_options = TRUE)
```

Row
-----------------------------------------------------------------------


### All consults

```{r}
plot_data <- ts %>%
  filter(type == 'Consult') %>%
  group_by(date) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'Consults')
```


### Underlying data

```{r}
prettify(plot_data, download_options = TRUE)
```


Row
-----------------------------------------------------------------------

### All tests

```{r}
plot_data <- ts %>%
  filter(type == 'Tested') %>%
  group_by(date) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'Tests')
```


### Underlying data


```{r}
prettify(plot_data, download_options = TRUE)
```

Row
-----------------------------------------------------------------------


### All treatments

```{r}
plot_data <- ts %>%
  filter(type == 'Treated') %>%
  group_by(date) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'People treated')
```


### Underlying data


```{r}
prettify(plot_data, download_options = TRUE)
```



By health facility
=====================================  

Row
-----------------------------------------------------------------------

### Cases

```{r}
plot_data <- ts %>%
  filter(type == 'Case') %>%
  group_by(date, health_post = gsub('Centro de Saude de ', '', health_post)) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'Cases') +
  facet_wrap(~health_post) +
  theme(axis.text.x = element_text(size = 5, angle = 90))
```


### Underlying data


```{r}
prettify(plot_data, download_options = TRUE)
```

Row
-----------------------------------------------------------------------


### Consults

```{r}
plot_data <- ts %>%
  filter(type == 'Consult') %>%
  group_by(date, health_post = gsub('Centro de Saude de ', '', health_post)) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'Consults') +
  facet_wrap(~health_post) +
  theme(axis.text.x = element_text(size = 5, angle = 90))

```


### Underlying data


```{r}
prettify(plot_data, download_options = TRUE)
```

Row
-----------------------------------------------------------------------

### Tests

```{r}
plot_data <- ts %>%
  filter(type == 'Tested') %>%
  group_by(date, health_post = gsub('Centro de Saude de ', '', health_post)) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'Tests') +
  facet_wrap(~health_post) +
  theme(axis.text.x = element_text(size = 5, angle = 90))

```


### Underlying data


```{r}
prettify(plot_data, download_options = TRUE)
```

Row
-----------------------------------------------------------------------


### Treatments

```{r}
plot_data <- ts %>%
  filter(type == 'Treated') %>%
  group_by(date, health_post = gsub('Centro de Saude de ', '', health_post)) %>%
  summarise(value = sum(value, na.rm = TRUE))
ggplot(data = plot_data,
       aes(x = date,
           y = value)) +
  geom_line(color = 'darkgreen', alpha = 0.7) +
  geom_point(color = 'darkgreen', alpha = 0.7) +
  geom_area(fill = 'darkgreen', color = NA, alpha = 0.2) +
  theme_maltem() +
  labs(x = 'Week',
       y = 'People treated') +
  facet_wrap(~health_post) +
  theme(axis.text.x = element_text(size = 5, angle = 90))

```


### Underlying data


```{r}
prettify(plot_data, download_options = TRUE)
```


Raw data
=====================================  

Row
-------------------------------------
  
### Time series

```{r}
prettify(ts, download_options = TRUE)
```

### API format

```{r}
prettify(api, download_options = TRUE)
```


Details
=====================================  

Row
-------------------------------------
  

### Data management

```{r}
flexdashboard::valueBox('Amone Felimone', icon = "fa-database",
         href="mailto:eldo.elobolobo@manhica.net?Subject=react%20dashboard")
```

### Visualization

```{r}
flexdashboard::valueBox('Joe Brew', icon = "fa-eye",
         href="mailto:joe@databrew.cc?Subject=react%20dashboard")
```

### Implementation and analysis

```{r}
flexdashboard::valueBox('Bea Galatas', icon = "fa-stethoscope",
         href="mailto:carlos.chaccour@isglobal.org?Subject=react%20dashboard")
```


Row
-------------------------------------
  

### Coordinating institution

```{r}
flexdashboard::valueBox('CISM', icon = "fa-users",
         href="http://www.manhica.org/wp/en/home-en/", color = 'warning')
```


### Collaborating institution

```{r}
flexdashboard::valueBox('ISGlobal', icon = "fa-group",
         href="http://www.isglobal.org", color = 'danger')
```

### Implementation

```{r}
flexdashboard::valueBox('MALTEM', icon = "fa-flag",
         href="http://www.manhica.org/wp/en/home-en/", color = 'info')
```
